\markdownRendererHeadingTwo{Lab Container (Lab 3a)}\markdownRendererInterblockSeparator
{}I have created a ``lab container'' to define the lab environment. You can use this container to try out some of the commands shown in this chapter. Directions for building and running the container are available in \markdownRendererLink{the included markdown file}{https://github.com/devsecfranklin/devsecops-tactical-workbook/tree/main/code/chapter-three/lab-3a.md}{https://github.com/devsecfranklin/devsecops-tactical-workbook/tree/main/code/chapter-three/lab-3a.md}{}. For now we don't have to be concerned about the syntax and composition of the Dockerfile. We will look more closely at Docker and Dockerfiles in an upcoming chapter.\markdownRendererInterblockSeparator
{}An advantage with executing lab commands in a container is we can try things without altering the configuration of our host operating system. The packages we install and configurations under test are, well, ephemeral!\markdownRendererInterblockSeparator
{}\markdownRendererHeadingThree{Build the Lab Container}\markdownRendererInterblockSeparator
{}\markdownRendererCodeSpan{sh
    docker build -t frank378:chapter-three \markdownRendererBackslash{}
    --build-arg BUILD\markdownRendererUnderscore{}DATE=\markdownRendererDollarSign{}(date -u +'\markdownRendererPercentSign{}Y-\markdownRendererPercentSign{}m-\markdownRendererPercentSign{}dT\markdownRendererPercentSign{}H:\markdownRendererPercentSign{}M:\markdownRendererPercentSign{}SZ') .
}\markdownRendererInterblockSeparator
{}\markdownRendererHeadingThree{Inspect the Lab Container}\markdownRendererInterblockSeparator
{}In this example, the container image ID is \markdownRendererCodeSpan{cdf6b6fafe03}. Substitue this string in your actual image build. The "docker inspect" command will return a great deal of information about the new container image in a JSON format.\markdownRendererInterblockSeparator
{}\markdownRendererCodeSpan{sh
\markdownRendererHash{}Successfully built cdf6b6fafe03  <-- substitue with the value from your docker build
docker inspect cdf6b6fafe03
docker images
}\markdownRendererInterblockSeparator
{}\markdownRendererHeadingTwo{Run the Lab Container}\markdownRendererInterblockSeparator
{}\markdownRendererCodeSpan{sh
docker run --rm  -it --entrypoint /bin/bash cdf6b6fafe03
}\markdownRendererInterblockSeparator
{}\markdownRendererHeadingTwo{Cleanup Lab Container}\markdownRendererInterblockSeparator
{}After you are finished working in the container, exit out and run these commands to delete the container and clean up the stale images.\markdownRendererInterblockSeparator
{}\markdownRendererCodeSpan{bash
docker image rm cdf6b6fafe03
docker system prune
}\relax